Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-09 02_Paper/paper.tex
Data preprocessing

Once enough data is collected, the next step is to clean the raw data and organize it accordingly. For our case, that means to merge the data collected from the two OPC-UA servers, and synchronize the time-stamp. Since our systems are not completely synchronized, it was needed to calculate the delta-time between servers by referencing each server's base clock. Once the delta-time was determined, a time-stamp function was implemented to correct the time-shift between samples and be able to merge all the data without incompatibilities.

Data tags interpretation is an important step in the preprocessing process. The raw data collected from the sensors is sometimes tagged by an alphanumeric code predefined by the sensor manufacture. To work with the data, it was needed to implement diverse functions which have the task to clean the raw data in a more human-readable form. This means to remove samples out of clear boundaries and missing values, as well as to translate the sensor code tags based on a dictionary predefined by the authors. This last step, might be optional in other implementations, however, it proves to be a great addition for testing purposes.

Once the data is clean and compiled in one directory, our step was to split the data based on the assembly cycle. For our purpose, we split the dataset into individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}. Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so. At this point, we have a series of data-samples based on time series. However, we are not interested in a time series analysis, therefore it was needed to compress each time-series based data-sample in an atemporal data-sample.
To eliminate time as a variable in our dataset, we defined a series of rules to be applied on each assembly cycle data-sample:

>>>>

Once enough data is collected, the next step is to clean the raw data and organize it accordingly \cite{goodfellow2016deep}. For our case, that means to merge the data collected from the two OPC-UA servers, and synchronize the time-stamp. Since our systems are not completely synchronized, it was needed to calculate the delta-time between servers by referencing each server's base clock. Once the delta-time was determined, a time-stamp function was implemented to correct the time-shift between samples and be able to merge all the data without incompatibilities.

Data tags interpretation is an important step in the preprocessing process \cite{goodfellow2016deep}. The raw data collected from the sensors is usually tagged by an alphanumeric code predefined by the sensor manufacture. To work with the data, it was needed to implement diverse functions which have the task to clean the raw data in a more human-readable form. This means to remove samples out of clear boundaries and missing values, as well as to translate the sensor code tags based on a dictionary predefined by the authors. This last step, might be optional in other implementations, however, it proves to be a great addition for testing purposes.

Once the data is clean and compiled in one directory, our step was to split the data based on the assembly cycle. For our purpose, we split the dataset into individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}. Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so. At this point, we have a series of data-samples based on time series. However, we are not interested in a time series analysis since we want to focus on ML methods based on an atemporal vector approach, therefore it was needed to compress each time-series based data-sample in an atemporal data-sample.
To eliminate time as a variable in our dataset, we defined a series of rules to be applied in each assembly cycle data-sample:
